### 2010-12-28 Documentation/atropos/atropos.tex
ENH: title change
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@715 fd2da0a4-d968-48df-9cb5-d8c496287cbf
ENH:  A few minor edits.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@716 fd2da0a4-d968-48df-9cb5-d8c496287cbf

\begin{center}
{\Large \bf An Open Source Framework for Multivariate $n$-Tissue
  Segmentation with Evaluation Using Open Data Sets} \\
\vspace*{0.5cm}
{\normalsize Brian B.~Avants$^{1*}$,  Nicholas J.~Tustison$^2$%
\symbolfootnote[1]{
  The first two authors contributed equally to this work.
}, 
Jue Wu$^1$, Philip A.~Cook$^1$, and James C.~Gee$^1$} \\
\begin{singlespace} 
{\scriptsize  $^1$ Penn Image Computing and Science Laboratory, University of Pennsylvania, Philadelphia, Pennsylvania,  USA.\\
  $^2$ Department of Radiology, University of Virginia, Charlottesville, Virginia, USA}
\end{singlespace}
\end{center}

@@

and the $(m,n)^{th}$ element of the covariance matrix, $\boldsymbol{\Sigma}$, is calculated from

@@

 \boldsymbol{\Sigma}_{mn,k} \leftarrow \frac{ \sum_{i=1}^N  ( \mathbf{y}_i - \boldsymbol{\mu}_k )^T p_k(l_k|\mathbf{y}_i) ( \mathbf{y}_i - \boldsymbol{\mu}_k )}{1 - \sum_{i=1}^N p^2_k(l_k|\mathbf{y}_i) }.

@@

\subsection{Likelihood Implementation}
As mentioned previously in the introduction, different groups have
opted for different likelihood models which have included either
parametric, specifically Gaussian, or nonparametric variations.
However, these approaches are similar in that they require a list
sample of intensity data from the input image(s) and a list of
weighting values for each observation of the list sample from which
the model is constructed.  In general, one may query model
probabilities by passing a given pixel's single intensity (for
univariate segmentation) or multiple intensities (for multivariate
segmentation) to the modeling function, regardless of whether the
function is parameter or non-parametric.  These similarities permitted
the creation of a generic plug-in architecture where classes
describing both parametric and nonparametric observational models are
all derived from an abstract list sample function class.  Three
likelihood classes have been developed, one parametric and two
nonparametric, and are available for usage although one of the
nonparametric classes is still in experimental development.  The
plug-in architecture even permits mixing likelihood models with
different classes during the same run for a hybrid
parametric/non-parametric model although this possibility has yet
to be fully explored.

>>>>

\begin{center}
{\Large \bf An Open-Source Multivariate Framework for $n$-Tissue
  Segmentation with Evaluation on Public Data} \\
\vspace*{0.5cm}
{\normalsize Brian B.~Avants$^{1*}$,  Nicholas J.~Tustison$^2$%
\symbolfootnote[1]{
  The first two authors contributed equally to this work.
}, 
Jue Wu$^1$, Philip A.~Cook$^1$, and James C.~Gee$^1$} \\
\begin{singlespace} 
{\scriptsize  $^1$ Penn Image Computing and Science Laboratory, University of Pennsylvania, Philadelphia, Pennsylvania,  USA.\\
  $^2$ Department of Radiology, University of Virginia, Charlottesville, Virginia, USA}
\end{singlespace}
\end{center}

@@

and the $k^{th}$ covariance matrix, $\boldsymbol{\Sigma}_k$, is calculated from

@@

 \boldsymbol{\Sigma}_{k} \leftarrow \frac{ \sum_{i=1}^N  p_k(l_k|\mathbf{y}_i) ( \mathbf{y}_{i} - \boldsymbol{\mu}_{k} )^{\mathrm{T}}  ( \mathbf{y}_{i} - \boldsymbol{\mu}_{k} )}{1 - \sum_{i=1}^N p^2_k(l_k|\mathbf{y}_{i}) }.

@@

\subsection{Likelihood Implementation}
As mentioned previously in the introduction, different groups have
opted for different likelihood models which have included either
parametric, specifically Gaussian, or nonparametric variations.
However, these approaches are similar in that they require a list
sample of intensity data from the input image(s) and a list of
weighting values for each observation of the list sample from which
the model is constructed.  In general, one may query model
probabilities by passing a given pixel's single intensity (for
univariate segmentation) or multiple intensities (for multivariate
segmentation) to the modeling function, regardless of whether the
function is parameter or non-parametric.  These similarities permitted
the creation of a generic plug-in architecture where classes
describing both parametric and nonparametric observational models are
all derived from an abstract list sample function class.  Three
likelihood classes have been developed, one parametric and one
nonparametric, and are available for usage although one of the
nonparametric classes is still in experimental development.  The
plug-in architecture even permits mixing likelihood models with
different classes during the same run for a hybrid
parametric/non-parametric model although this possibility has yet
to be fully explored.
